### 2020-01-30 wuhan.tex
push

Since December 2019, the novel coronavirus (2019-nCoV) has been
spreading in China and other parts of the world.
As of January 28th, 2020, the World Health Organization has
confirmed 4593 cases, including 56 confirmed cases in 14 different
countries, outside China \citep{who28report}.
Although the virus is believed to have originated
from animal reservoirs, a recent case from Viet Nam
demonstrated its ability to directly transmit between
humans \citep{who26report},
posing a greater threat for its spread.
\jd{It is spread primarily from person to person; that's been obvious for a while and is now confirmed. We should find a better cite and leave Viet Nam out of it.}

>>>>

Since December 2019, the novel coronavirus (2019-nCoV) has been spreading in China and other parts of the world.
As of January 28th, 2020, the World Health Organization has confirmed 4593 cases, including 56 confirmed cases in 14 different countries, outside China \citep{who28report}.
Although the virus is believed to have originated from animal reservoirs \citep{cdcncov}, 
there is clear evidence that it can be directly tranmitted between humans,
posing a greater threat for its spread.
\jd{It is spread primarily from person to person; that's been obvious for a while and is now confirmed. We should find a better cite and leave Viet Nam out of it.}
